Search for Spatially Extended \fermi-LAT Sources Using Two Years of Flight Data

### 2011-08-23 extended_catalog/paper/extended_catalog.tex
additions

A number of astrophysical sources classes including supernova remnant
(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
galaxy clusters could be expected to spatially resolvable at \gev
energies.  Dark matter satellites are also hypothesized to be seen
as spatially extended at \gev energies.  The LAT Collaboration has
previously reported on five SNRs which are spatially extended beyond
the LAT PSF at \gev energies (IC443, W28, W44, W51C, and RX J1713.7-3946
\citep{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended PWNe
were detected as being extended: MSH 15-52, Vela~X, and HESS\,J1825-137
\citep{msh1552,velax,fermi_hess_j1825}. Two close-by galaxies the Large
and Small Magalenic Clouds and one radio galaxy Centarus A were spatially
resolved at \gev energies \citep{lmc,smc,cen_a_lat}.  Furthermore,
a number of other sources previously detected at \gev energies are
positionally coincident with sources that exhibit extension at other
wavelengths and could be expected to be spatially resolvable at \gev
energies.

At \tev energies many sources have been recently detected as
begin spatially extended using air Cherenkov detectors.  Most
prominent was a survey of the Galactic plane using the High Energy
Stereoscopic System (H.E.S.S) which reported 14 spatially extended
sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
sources detected at \tev energies (most notably the $\gamma$-ray binaries
LS\,5039 \citep{HESSLS5039}, LS I+61-303 \citep{MAGICLSI, VERITASLSI}
HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
have no significant extension detected.  High energy $\gamma$-rays from
these sources are produced by the decay of $\pi^0$s produced by hadronic
interactions with interstellar matter and by relativistic electrons
due to Inverse Compton (IC) scattering and Bremsstrahlung radiation
\citep{blandford_and_eichler_1987}.  It is likely that the \gev and
\tev emission from these sources originates from the same population of
high-energy particles and so at least some of these sources should be
detected as extended sources at \gev energies.  Studying 
these \tev sources at \gev energies would help to
determine the emission mechanisms producing these high energy photons.

The Large Area Telescope (LAT) is a pair conversion telescope on the
{\em \fermi Gamma-ray Space Telescope} (\fermi) that been surveying the
$\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large
effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  Using two years of
all-sky surveying data, the LAT Collaboration published a catalog of 1873
sources detected at these \gev energies called 2FGL \citep{second_cat}.
The counterparts of many of these sources can be spatially resolved
when observed at other frequencies but detecting the spatial extension
of these sources at \gev energies is difficult because the size of the
point-spread function (PSF) of the LAT is comparable to the typical size
of many of these sources.

On the other hand, the capability to spatially resolve \gev $\gamma$-ray
sources is important for several reasons.  First, multiple potential
counterparts detected at other frequencies exist within the localization
confidence region of a typical LAT source along the Galactic plane.
Finding a coherent source extension across different energy bands can
help to associate a LAT source to an otherwise confused counterpart.
Furthermore, dark matter satellite in our galaxy have been predicted to be
detected and spatially extended at \gev energies and could be discovered
outside the galactic plane \citep{pre_luanch_dark_matter_fermi}.  Also,
due to the strong energy dependence of the LAT PSF, the spatial and
spectral information about a source do not simply decouple. An inaccurate
spatial model will bias the spectral model of the source. Specifically,
modeling a spatially extended source as point-like will systematically
shift a spectral analysis to softer indices. Furthermore, correctly
modeling a source's extension is important for improving the model of
the sky and removing excess residuals, for example in the region around
surrounding the Large Magellanic Clouds \citep{first_cat}.  Such excess
residuals potentially bias the significance and measured spectrum of
neighboring sources in the densely populated Galactic plane.

@@

Our analysis technique is closely related to that 
of the 2FGL catalog. We used the same two-year dataset from 2008 August 4
to 2010 August 1 and we used the same P7\_V6 Source class
event selection and IRFs \citep{lat_on_orbit_psf}.  
The same 
models were used to describe the background from Galactic diffuse, isotropic, and
Earth limb emission.  To account for possible residuals in the diffuse
emission model, the galactic emission was scaled by a unitless power-law
and the isotropic component's normalization was left free.

As was shown in Section~\ref{extension_sensitivity}, we gain little in sensitivity using photons with energies
below 1 \gev. On the other hand, the large PSF at low energy makes us
more susceptible to systematic errors arising from source confusion due
to multiple point sources and susceptible to incorrect modeling of the
Galactic diffuse emission. In addition, the Galactic diffuse emission
is more pronounced at lower energies due to its steep energy spectrum.
For that reason, we performed our search using only photons with
energies between 1 \gev and 100 \gev.

We also performed a search for extended sources using only 10-100 \gev photons. 
Even though we are testing the same
sources, this approach is complimentary because the Galactic diffuse
emission is even less dominant above 10 \gev. Furthermore, source
confusion becomes less of a problem since most LAT sources are not
significantly detected at energies exclusively above 10 \gev. So we
expect to be able to resolve harder sources in more complicated regions. The $>10$ \gev
analysis is
especially
beneficial for regions near pulsars which are not significantly above 10 \gev and was
successfully used in detecting HESS\,J1825-137 and MSH 15-52 with the LAT
\citep{msh1552,fermi_hess_j1825}.

We tested each source for extension using
\pointlike
assuming the source had a uniform radially symmetric surface brightness
and a power-law spectral model.
We used a circular $10\deg$ region of interest centered on our source and
included all catalog sources within $15\deg$ of the source of interest
in our background model.
We refit the spectral parameters of sources within $2\deg$ of the source
to avoid potential biases of the extension parameters of the source of
interest due to close-by background sources.

Finally, when analyzing the region, we automatically removed other 2FGL
sources which were within 0\fdg5 of the source of interest. This was
done to avoid a concern that extended sources are included in 2FGL as
multiple point sources. These spurious sources could distort the
extension fit.  Instead, when a source is found to be significantly
extended (i.e. $\tsext>16$), we perform the dual localization procedure
(described in Section~\ref{dual_localization_method} to compare the
extended source hypothesis to the hypothesis of two independent point
sources. Only sources with $\tsext>\tsinc$ are considered as extended.

@@

Based on size vs. physical distance considerations,
we expect most extended sources to be located inside our Galaxy
adn thus to be concentrated along the Galactic plane.  Unfortunately, the \gev emission
in the Galactic plane is dominated by extremely structured 
diffuse emission from the interactions of cosmic rays with the
interstellar medium.  Finding sources on top of this emission is difficult
\citep{first_diffuse_paper} as has been discussed in 1FGL and 2FGL
\citep{first_cat,second_cat}.  Furthermore, the Galactic plane is crowded
and it is often difficult to correctly model nearby sources.  Because of this,
finding a source with $\tsext>16$ is not a sufficient
criteria for resolving a source. For each extended source,
we perform several analysis crosschecks.

For each candidate, we generated a map of residual \ts by adding a new
source of spectral index 2 into the region and finding the increase in
likelihood when fitting its flux. \ts maps are useful to look for residual
structure in the sky model.  Figure~\ref{res_tsmaps} shows a residual \ts
map for the extended source IC443.  The residual \ts map indicates that
the spatially extended model for IC443 is a significantly better description
of the observed photons.
We also generated plots of the sum of
all counts within a given distance of the source and compared it to the
model predictions of a point source.  
An example radial integral plot is shown for the extended source IC443
in Figure~\ref{four_plots_ic443}.  For each source, we also made
diffuse-emission-subtracted smoothed counts
maps. Figure~\ref{four_plots_ic443} also shows an example for IC443.

% 2FGL J1856.2+0450c = P72Y3047 for
We then inspected the residual \ts, smoothed counts maps, and radial
integral distributions to identify cases in which the extension fit
is clearly influenced by large-scale residuals in the diffuse emission
and hence the extension measurement unreliable.  An example of such a
case is shown in Figure~\ref{example_bad_fit}. It shows a Galactic and
isotropic diffuse-emission-subtracted smoothed counts map of this source
using 1-100 \gev photons.  In this region along the Galactic plane,
there appears to be large-scale residual in the diffuse emission. As
a result, 2FGL\,J1856.2+0450c fit to an extension of 1\fdg83 and the
result is statistically significant with \tsext=45.4. However, by looking at
the residuals it is clear that this complicated region is not fit well
even though the source's extension is statistically significant. We do
not report sources as extended that fail this inspection.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

Because of the high source density in the Galactic plane, for promising
candidates we often had to iteratively improve the model of our background
sources to obtain a better fit of the sources.  Several catalog
sources would often fill in the emission of the extended source and would
have to be removed from the region.  Similarly, background sources
were often insignificant in the fit energy range and had to be removed.
The position of background sources would often have to be refit once the
extended source was fit.  When the model of the extended source coupled
strongly with nearby sources, we iteratively fit the extended source and
all nearby sources until the fit converged.  For each extended source,
we describe the modifications of the background model compared to the model
used in the creation of the 2FGL catalog that were required.

@@

We estimate a systematic error on the extension of a source due to
uncertainty in our knowledge of the LAT PSF.  Before
launch, the LAT PSF was determined by a detector simulation which was
verified in accelerator tests \citep{atwood_LAT_mission}. However,
in-flight data revealed a discrepancy
above a few \gev in the PSF compared to the
photon angular distribution of bright AGN.  A publication on this issue is in preparation
\citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit empirically to
bright AGN and this empirical parameterization is the default PSF used
in the P7\_V6 IRFs.  To account for this uncertainty in our knowledge of
the PSF, we refit our extended source candidates using the Monte Carlo
representation of the PSF and consider the difference in extension found
using the two PSFs as a systematic error on the extension of a source.
The same approach was used in
\citep{ic443}.  At high energies, we believe that our parameterization
of the PSF from bright AGN is substantially better than the Monte Carlo
representation of the PSF so this estimate of systematic errors is conservative.

@@

We estimate a second systematic error on the extension of a source
due to uncertainty in the model of the Galactic diffuse emission by
using an alternative diffuse model. An alternative model was based upon
GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy. See \url{http://galprop.stanford.edu/} for details and
references} and used in the LAT analysis of the isotropic diffuse
emission \citep{isotropic_lat}.  
The intensities of various components to the galactic
diffuse emission are then fitted individually using a spatial
distribution of the intensities within the ROI 
as predicted by the model.
We distinguish contributions from CR interactions with
the molecular hydrogen, the atomic+ionized hydrogen,
residual gas traced by dust \citep{isabelle_dark_gass},
and the interstellar radiation field. We further
split the contributions from interactions with molecular
and atomic hydrogen to the
Galactic diffuse emission according
to the distance from the Galactic center in
which they are produced. Hence, we replace
the standard diffuse emission model by 18
individually fitted templates to describe individual
components of the diffuse emission.
A similar crosscheck was used in the
LAT Collaboration's analysis of RX J1713.7-3946 \citep{rx_j1713_lat}.

It is not expected that this diffuse model is superior to the standard
LAT model that was obtained through an all-sky fit.  But adding degrees of freedom to the background model can
remove likely spurious sources that correlate with features in the
Galactic diffuse emission.  Therefore, this tests systematics that may
be due to incorrect modeling of the diffuse emission in the region.

@@

We first present on our analysis of the twelve extended sources
included in 2FGL.
\citep{second_cat}.
The six extended SNRs IC443, W28, W30, W44, W51C, and the
Cygnus Loop were included in 2FGL.  IC443, W28, W44, W51C, and the
Cygnus Loop were
first reported in \cite{ic443,w28,w44,w51c,cygnus_loop_lat}.  A
detailed publication by the LAT
Collaboration about W30 is still in preparation.
\gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
Using 1-100 \gev photons, our analysis significantly detected the
extension of all six SNRs.
% 2 galaxies

Two nearby satellite galaxies of the Milky Way the Large Magalenic Cloud (LMC)
and the Small Magalenic
Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
detected using 1-100 \gev photons. Our
fit extension is comparable to the published result, but we note that
previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
brightness spatial model when fitting it (\citep{lmc}).

% 3 PWN
Three PWNe Vela X, MSH 15-52, and HESS\,J1825-137 were
already identified in 2FGL \citep{velax,msh1552,fermi_hess_j1825}.  
HESS\,J1825-137 was significantly detected using 10-100 \gev photons.
To improve the model of this source, we removed the
nearby catalog source 2FGL\,J1823.1-1338c which is part of the extended
source.  To avoid confusion with the nearby bright pulsar PSR J1509-5850, MSH 15-52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH 15-52 to be consistent with the published
size with an extension significance of \tsext=6.5.

@@

Our analysis of these sources is summarized in
Table~\ref{known_extended_sources}.  This table includes the best fit
position and extension of these sources when fitting them as disk-shaped
sources with a radially symmetric uniform surface brightness. It also
includes the best fit spectral parameters for each source.  The position
and extension of Vela X and the Centaurus A Lobes are included in this
list for completeness.

@@

\subsection{2FGL\,J0823.0-4246}
\label{section_2FGL_J0823.0-4246}

@@

The source 2FGL\,J0823.0-4246 was found 
using 1-100 \gev photons to have an 
extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
with an extension
significance of $\tsext=46.3$.  The source was fit to a position of
$(l,b)=(260\fdg32,-3\fdg28)$.  
This source is coincident with the one-year
catalog source 1FGL\,J0823.3-4248.
\hl{
Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source
and Figure~\ref{snr_seds} shows the LAT spectrum of it.
}

To get a good fit of the source, we had to remove the nearby catalog
sources 2FGL\,J0823.4-4305 and 2FGL\,J0821.0-4254 which are part of the
extended source.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
we conclude that this is an extended source.  These modifications are
shown in Figure~\ref{1FGL_J0823.3-4248}.

@@

\subsection{2FGL\,J1627.0-2425c}
\label{section_2FGL_J1627.0-2425c}

@@

The source 2FGL\,J1627.0-2425c was found using 1-100 \gev photons to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$.  The best fit position is
$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
year catalog source 1FGL\,J1628.6-2419c.  A counts map showing this source
is seen in Figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=20.0$
is smaller than \tsext, we conclude that this is an extended source.

@@

\subsection{2FGL\,J1712.4-3941}
\label{section_2FGL_J1712.4-3941}

@@

The source 2FGL\,J1712.4-3941 was found using 1-100 \gev
photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
with an extension significance of $\tsext=39.6$.  This source was
fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
is coincident with the one-year catalog source 1FGL\,J1711.7-3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

This source is spatially coincident with the SNR RX J1713.7-3946
and was recently reported by \citep{rx_j1713_lat}.  
Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR RX
J1713.7-3946 from \citep{rx_j1713_hess}.  To analyze this source,
we used the same background model as the recent LAT publication.
2FGL\,J1715.4-4024c is spatially coincident with Source A and was
moved to $(\text{RA},\text{Dec})=(258.84,-40.46)$. Source B was added
at $(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
$(\text{RA},\text{Dec})=(257.47,-39.75)$.

\subsection{2FGL\,J0851.7-4635}
\label{section_2FGL_J0851.7-4635}

@@

The source 2FGL\,J0851.7-4635 was found 
using 10-100 \gev photons to have an
extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
with an extension
significance of $\tsext=87.2$.  The source was fit to a position of
$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

2FGL\,J0851.7-4635 is spatially coincident with the SNR Vela Jr.
Overlaid on Figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
\tev by H.E.S.S \citep{vela_jr_hess}.  The \gev and \tev morphology
match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
in preparation.

>>>>

A number of astrophysical sources classes including supernova remnant
(SNRs), pulsar wind nebulae (PWNe), molecular clouds, normal galaxies,
galaxy clusters could be expected to spatially resolvable at \gev
energies.  Dark matter satellites are also hypothesized to be seen
as spatially extended at \gev energies.  The LAT Collaboration has
previously reported on five SNRs which are spatially extended beyond
the LAT PSF at \gev energies (IC443, W28, W44, W51C, and RX\,J1713.7$-$3946
\citep{ic443,w28,w44,w51c,rx_j1713_lat}). In addition, three extended PWNe
were detected as being extended: MSH\,15$-$52, Vela~X, and HESS\,J1825$-$137
\citep{msh1552,velax,fermi_hess_j1825}. Two close-by galaxies the Large
and Small Magalenic Clouds and one radio galaxy Centarus A were spatially
resolved at \gev energies \citep{lmc,smc,cen_a_lat}.  Furthermore,
a number of other sources previously detected at \gev energies are
positionally coincident with sources that exhibit extension at other
wavelengths and could be expected to be spatially resolvable at \gev
energies.

At \tev energies many sources have been recently detected as
begin spatially extended using air Cherenkov detectors.  Most
prominent was a survey of the Galactic plane using the High Energy
Stereoscopic System (H.E.S.S) which reported 14 spatially extended
sources with extensions varying from $\sim0\fdg1$ to $\sim0\fdg25$
\citep{hess_plane_survey}.  In fact, within our Galaxy only very few
sources detected at \tev energies (most notably the $\gamma$-ray binaries
LS\,5039 \citep{HESSLS5039}, LS I+61$-$303 \citep{MAGICLSI, VERITASLSI}
HESS\,J0632+057 \citep{HESS0632}, and the Crab nebula \citep{crab_weekes})
have no significant extension detected.  High energy $\gamma$-rays from
these sources are produced by the decay of $\pi^0$s produced by hadronic
interactions with interstellar matter and by relativistic electrons
due to Inverse Compton (IC) scattering and Bremsstrahlung radiation
\citep{blandford_and_eichler_1987}.  It is likely that the \gev and
\tev emission from these sources originates from the same population of
high-energy particles and so at least some of these sources should be
detected as extended sources at \gev energies.  Studying 
these \tev sources at \gev energies would help to
determine the emission mechanisms producing these high energy photons.

The Large Area Telescope (LAT) is a pair conversion telescope on the
{\em \fermi Gamma-ray Space Telescope} (\fermi) that been surveying the
$\gamma$-ray sky since 2008 June.  The LAT has broad energy coverage
(20 \mev to $>300$ \gev), wide field of view ($\sim 2.4 \sr$), and large
effective area ($\sim 8000\ \cm^2$ at $>1 \gev$).  
Using one year of all-sky surveying data, the LAT Collaboration published
a catalog of 1451 sources significantly detected at \gev energies called 1FGL \citep{first_cat}.
Using two years of data, a second catalog called 2FGL reported on 1873
sources \citep{second_cat}.
The counterparts of many of these sources can be spatially resolved
when observed at other frequencies but detecting the spatial extension
of these sources at \gev energies is difficult because the size of the
point-spread function (PSF) of the LAT is comparable to the typical size
of many of these sources.

The capability to spatially resolve \gev $\gamma$-ray
sources is important for several reasons.  First, multiple potential
counterparts detected at other frequencies exist within the localization
confidence region of a typical LAT source along the Galactic plane.
Finding a coherent source extension across different energy bands can
help to associate a LAT source to an otherwise confused counterpart.
Furthermore, dark matter satellite in our galaxy have been predicted to be
detected and spatially extended at \gev energies and could be discovered
outside the galactic plane \citep{pre_luanch_dark_matter_fermi}.  Also,
due to the strong energy dependence of the LAT PSF, the spatial and
spectral information about a source do not simply decouple. An inaccurate
spatial model will bias the spectral model of the source. Specifically,
modeling a spatially extended source as point-like will systematically
shift a spectral analysis to softer indices. Furthermore, correctly
modeling a source's extension is important for improving the model of
the sky and removing excess residuals, for example in the region around
surrounding the Large Magellanic Clouds \citep{first_cat}.  Such excess
residuals potentially bias the significance and measured spectrum of
neighboring sources in the densely populated Galactic plane.

@@

Our analysis technique is closely related to that 
of the 2FGL catalog. We used the same two-year dataset from 2008 August 4
to 2010 August 1 and we used the same P7\_V6 Source class
event selection and IRFs \citep{lat_on_orbit_psf}.  
The same 
models were used to describe the background from Galactic diffuse, isotropic, and
Earth limb emission.  To account for possible residuals in the diffuse
emission model, the galactic emission was scaled by a power-law
and the isotropic component's normalization was left free.

As was shown in Section~\ref{extension_sensitivity}, we gain little in sensitivity using photons with energies
below 1 \gev. On the other hand, the large PSF at low energy makes us
more susceptible to systematic errors arising from source confusion due
to multiple point sources and modeling of the
Galactic diffuse emission. In addition, the Galactic diffuse emission
is more pronounced at lower energies due to its steep energy spectrum
\citep{intermediate_diffuse_lat}.
For that reason, we performed our search using only photons with
energies between 1 \gev and 100 \gev.

We also performed a search for extended sources using only 10 \gev to 100 \gev photons. 
Even this approach tests the same
sources, it is complimentary because the Galactic diffuse
emission is even less dominant above 10 \gev. Furthermore, source
confusion becomes less of a problem since most LAT sources are not
significantly detected at energies exclusively above 10 \gev. So we
expect to be able to resolve harder sources in more complicated regions. The $>10$ \gev
analysis is
especially
beneficial for regions near pulsars which are not significantly detected 
above 10 \gev. A similar procedure was
used to detect HESS\,J1825$-$137 and MSH\,15$-$52 with the LAT
\citep{msh1552,fermi_hess_j1825}.

We tested each source for extension using
\pointlike
assuming the source had a uniform radially symmetric surface brightness
and a power-law spectral model.
We used a circular $10\deg$ region of interest (ROI) centered on our source and
included all catalog sources within $15\deg$ of the source of interest
in our background model.
We refit the spectral parameters of sources within $2\deg$ of the source
to avoid potential biases of the extension parameters of the source of
interest due to close-by background sources.

Finally, when analyzing each region, we automatically removed from
our background model other 2FGL sources which were within 0\fdg5 of
the source of interest from the background model. This was done due
to a concern that extended sources are included in 2FGL as multiple
point sources. These spurious sources could distort the extension
fit.  Instead, when a source is found to be significantly extended
(i.e. $\tsext>16$), we perform the dual localization procedure (described
in Section~\ref{dual_localization_method} to compare the extended source
hypothesis to the hypothesis of two independent point sources. Only
sources with $\tsext>\tsinc$ are considered as extended.

@@

We expect most spatially resolvable extended sources to be located
in our Galaxy and thus to be concentrated along the Galactic plane.
Unfortunately, the \gev emission in the Galactic plane is dominated by
extremely structured diffuse emission from the interactions of cosmic rays
with the interstellar medium.  Finding sources on top of this emission
is difficult \citep{first_diffuse_paper} as has been discussed in 1FGL
and 2FGL \citep{first_cat,second_cat}.  Furthermore, the Galactic plane
is crowded and it is often difficult to correctly model nearby sources.
Because of this, finding a source with $\tsext>16$ is not a sufficient
criteria alone for claiming a detection of source extension.  For each
extended source, we perform several analysis crosschecks.

For each candidate, we generated a map of residual \ts by adding a new
source of spectral index 2 into the region at each pixel and finding the
increase in likelihood when fitting its flux. Residual \ts maps are useful
to look for residual structure in the sky model.  Figure~\ref{res_tsmaps}
shows a residual \ts map for the extended source IC443.  The residual
\ts map indicates that the spatially extended model for IC443 is a
significantly better description of the observed photons.  We also
generated plots of the sum of all counts within a given distance of
the source and compared it to the model predictions of a point source.
An example radial integral plot is shown for the extended source
IC443 in Figure~\ref{four_plots_ic443}.  For each source, we also made
diffuse-emission-subtracted smoothed counts maps (show for IC443 in
Figure~\ref{four_plots_ic443}).

% 2FGL J1856.2+0450c = P72Y3047 for
We then inspected each extended source candidate to identify cases in
which the extension fit is clearly influenced by large-scale residuals in
the diffuse emission and hence the extension measurement is unreliable.
An example of such a case is shown in Figure~\ref{example_bad_fit}. It
shows a Galactic and isotropic diffuse-emission-subtracted smoothed
counts map of 2FGL\,J1856.2+0450c using 1 \gev to 100 \gev photons.
In this region along the Galactic plane, there appears to be large-scale
residual in the diffuse emission. As a result, 2FGL\,J1856.2+0450c is fit
to an extension of 1\fdg83 and the result is statistically significant
with \tsext=45.4. However, by looking at the residuals it is clear
that this complicated region is not fit well even though the source's
extension is statistically significant. We do not report sources that
fail this inspection as extended.
% information came from
% /nfs/slac/g/ki/ki03/lande/extended_catalog/2FGL/v15/standard_analysis/spectral_emin_1000_v1/P72Y3047/v1/results_followup_P72Y3047.yaml

@@

Because of the high source density in the Galactic plane, we often had
to iteratively improve the model of our background sources to obtain a
better fit of the candidate source.  Several catalog sources would often
fill in the emission of the extended source and had to be removed from
the background model of the region.  Similarly, background sources were
often insignificant in the fit energy range and had to be removed from
the sky model.  The position of background sources would often have
to be refit once the extended source was fit.  When the model of the
extended source coupled strongly with nearby sources, we iteratively
fit the extended source and all nearby sources until the fit converged.
For each extended source, we describe the modifications of the background
model compared to the model used in the creation of the 2FGL catalog
that were required.

@@

We estimate a systematic error on the extension of a source due to
uncertainty in our knowledge of the LAT PSF.  Before launch, the LAT
PSF was determined by detector simulations which were verified in
accelerator tests \citep{atwood_LAT_mission}. However, in-flight data
revealed a discrepancy above a few \gev in the PSF compared to the 
angular distribution of photons from bright AGN.  A publication on this issue is in
preparation \citep{lat_on_orbit_psf}.  Subsequently, the PSF was fit
empirically to bright AGN and this empirical parameterization is the
default PSF used in the P7\_V6 IRFs.  To account for this uncertainty in
our knowledge of the PSF, we refit our extended source candidates using
the pre-flight Monte Carlo representation of the PSF and consider the difference
in extension found using the two PSFs as a systematic error on the
extension of a source.  The same approach was used in \citep{ic443}.
At high energies, we believe that our parameterization of the PSF from
bright AGN is substantially better than the Monte Carlo representation
of the PSF so this estimate of systematic errors is conservative.

@@

We estimate a second systematic error on the extension of a source
due to uncertainty in the model of the Galactic diffuse emission by
using an alternative diffuse model. An alternative model was based
upon GALPROP\footnote{GALPROP is a software package for calculating the
Galactic $\gamma$-ray emission based on a model of cosmic-ray propagation
in the Galaxy. See \url{http://galprop.stanford.edu/} for details
and references} and used in the LAT analysis of the isotropic diffuse
emission \citep{isotropic_lat}.  The intensities of various components
to the galactic diffuse emission were then fitted individually using a
spatial distribution of the intensities within the ROI as predicted by
the model.  We distinguish contributions from CR interactions with the
molecular hydrogen, the atomic+ionized hydrogen, residual gas traced
by dust \citep{isabelle_dark_gass}, and the interstellar radiation
field. We further split the contributions from interactions with molecular
and atomic hydrogen to the Galactic diffuse emission according to the
distance from the Galactic center in which they are produced. Hence, we
replace the standard diffuse emission model by 18 individually fitted
templates to describe individual components of the diffuse emission.
A similar crosscheck was used in the LAT Collaboration's analysis of 
RX\,J1713.7$-$3946 \citep{rx_j1713_lat}.

It is not expected that this diffuse model is superior to the standard
LAT model obtained through an all-sky fit.  However, adding degrees of freedom to the background model can
remove likely spurious sources that correlate with features in the
Galactic diffuse emission.  Therefore, this tests systematics that may
be due to incorrect modeling of the diffuse emission in the region.

@@

We first present on our analysis of the twelve extended sources
included in 2FGL.
\citep{second_cat}.
Six extended SNRs were included in 2FGL: IC443, W28, W30, W44, W51C, and the
Cygnus Loop \citep{ic443,w28,w44,w51c,cygnus_loop_lat}.\footnote{A
detailed publication by the LAT
Collaboration about W30 is still in preparation.}
\gev emission from W30 was also studied in \cite{castro_and_slane_2010}.
Using 1 \gev to 100 \gev photons, our analysis significantly detected the
extension of all six SNRs.
% 2 galaxies

Two nearby satellite galaxies of the Milky Way the Large Magalenic Cloud (LMC)
and the Small Magalenic
Cloud (SMC) were included in 2FGL as spatially extended sources \citep{lmc,smc}.  They were significantly
detected using 1 \gev to 100 \gev photons. Our
fit extension is comparable to the published result, but we note that
previous LAT Collaboration publication on LMC used a more complicated two 2D Gaussian surface
brightness spatial model when fitting it (\citep{lmc}).

% 3 PWN
Three PWNe, MSH\,15$-$52, Vela X, and HESS\,J1825$-$137 were
identified in 2FGL \citep{msh1552,velax,fermi_hess_j1825}.  
HESS\,J1825$-$137 was significantly detected using 10 \gev to 100 \gev photons.
To improve the model of this source, we removed from our background model the
nearby catalog source 2FGL\,J1823.1$-$1338c which is part of the extended
source.  To avoid confusion with the nearby bright pulsar PSR\,J1509$-$5850, MSH\,15$-$52 must be
analyzed at high energies.  Using photons with energies above 10 \gev,
we fit the extension of MSH\,15$-$52 to be consistent with the published
size with an extension significance of \tsext=6.5.

@@

Our analysis of these sources is summarized in
Table~\ref{known_extended_sources}.  This table includes the best fit
position and extension of these sources when fitting them as disk-shaped
sources with a radially symmetric uniform surface brightness. It also
includes the best fit spectral parameters for each source.  The position
and extension of Vela X and the Centaurus A Lobes are taken from
\cite{velax,cen_a_lat} and are included in this list for completeness.

@@

\subsection{2FGL\,J0823.0$-$4246}
\label{section_2FGL_J0823.0-4246}

@@

The source 2FGL\,J0823.0$-$4246 was found 
using 1-100 \gev photons to have an 
extension of $0\fdg37\pm0\fdg03_\stat\pm0\fdg02_\sys$ 
with an extension
significance of $\tsext=46.3$.  The source was fit to a position of
$(l,b)=(260\fdg32,-3\fdg28)$.  
This source is coincident with the one-year
catalog source 1FGL\,J0823.3$-$4248.
\hl{
Figure~\ref{1FGL_J0823.3-4248} shows a
counts map of this source
and Figure~\ref{snr_seds} shows the LAT spectrum of it.
}

To get a good fit of the source, we had to remove from our background
model the nearby catalog
sources 2FGL\,J0823.4$-$4305 and 2FGL\,J0821.0$-$4254 which are part of the
extended source.  We tested the source for source confusion by fitting
it as two point sources. Because $\tsinc=22.1$ is smaller then \tsext,
we conclude that this is an extended source.  These modifications are
shown in Figure~\ref{1FGL_J0823.3-4248}.

@@

\subsection{2FGL\,J1627.0$-$2425c}
\label{section_2FGL_J1627.0-2425c}

@@

The source 2FGL\,J1627.0$-$2425c was found using 1-100 \gev photons to
have an extension of $0\fdg41\pm0\fdg05_\stat\pm0\fdg02_\sys$ with
an extension significance of $\tsext=31.1$.  The best fit position is
$(l,b)=(353\fdg08, 16\fdg78)$.  This source is coincident with the one
year catalog source 1FGL\,J1628.6$-$2419c.  A counts map showing this source
is seen in Figure \ref{1FGL_J1628.6-2419c}.  To test for source confusion,
we also fit the source instead as two point sources. Since $\tsinc=20.0$
is smaller than \tsext, we conclude that this is an extended source.

@@

\subsection{2FGL\,J1712.4$-$3941}
\label{section_2FGL_J1712.4-3941}

@@

The source 2FGL\,J1712.4$-$3941 was found using 1-100 \gev
photons to have an extension $0\fdg56\pm0\fdg04_\stat\pm0\fdg02_\sys$
with an extension significance of $\tsext=39.6$.  This source was
fit to a position of $(l,b)=(347\fdg25,-0\fdg54)$.  The source
is coincident with the one-year catalog source 1FGL\,J1711.7$-$3944c.
Figure \ref{2FGL_J1712.4-3941} shows a smoothed counts map of this source.

This source is spatially coincident with the SNR RX\,J1713.7$-$3946
and was recently reported by \citep{rx_j1713_lat}.  
Figure~\ref{2FGL_J1712.4-3941} overlays H.E.S.S. \tev contours of SNR 
RX\,J1713.7$-$3946 from \citep{rx_j1713_hess}.  To analyze this source,
we used the same background model as the recent LAT publication.
2FGL\,J1715.4$-$4024c is spatially coincident with Source A and was
moved to $(\text{RA},\text{Dec})=(258.84,-40.46)$. Source B was added
at $(\text{RA},\text{Dec})=(258.71,-38.70)$ and Source C was added at
$(\text{RA},\text{Dec})=(257.47,-39.75)$.

\subsection{2FGL\,J0851.7$-$4635}
\label{section_2FGL_J0851.7-4635}

@@

The source 2FGL\,J0851.7$-$4635 was found 
using 10-100 \gev photons to have an
extension of $1\fdg13\pm0\fdg08_\stat\pm0\fdg05_\sys$ 
with an extension
significance of $\tsext=87.2$.  The source was fit to a position of
$(l,b)=(266\fdg29,-1\fdg43)$.  Figure~\ref{Vela_Jr} shows a counts
map of this source.

2FGL\,J0851.7$-$4635 is spatially coincident with the SNR Vela Jr.
Overlaid on Figure~\ref{Vela_Jr} are contours of Vela Jr. as seen in
\tev by H.E.S.S \citep{vela_jr_hess}.  The \gev and \tev morphology
match well.  A detailed papers by the LAT Collaboration on Vela Jr. is
in preparation.
